Global Climate of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and Spitzer Phase Curve Observations

### 2017-10-25 ms.tex
spectra blah
new fig
table
table!
formula

@@

%The apparent low amplitude variability is likely due to rotational modulation in the visibility of weak, magnetic surface features \citep[see, e.g.,][]{hfh1995}.

%This implies there can be very little night-to-night variability in WASP-103. The three seasonal mean brightness values given in column 5 scatter about their grand mean with a standard deviation of 0.0036 mag, but we note that the most discrepant mean is from the third season, for which we have only partial coverage. Therefore, our results do not completely rule out low-level, year-to-year variability of 0.001~mag or so.

%We performed periodogram analyses of the individual observing seasons and the complete dataset and found no significant periodicity.  To maximize the possibility of detecting a rotation signal in WASP-103, we normalized the dataset by adding a constant offset to the second and third observing seasons to have the same mean as the first. 
%To first order, this removes possible long-term variability in WASP-103 and/or the comparison stars as well as any uncorrected, long-term systemmatic effects.  It is the normalized data that are plotted in the top panel of Fig.~1.

%We performed a least-squares fit to the data with a sine curve with trial frequencies between 0.005 and 0.95 c/d, corresponding to periods between one and 200 days. The goodness of fit at each frequency is measured as the reduction factor in the variance of the original data.  The result suggests low-amplitude brightness variability in WASP-103 with a period near 6.814 days.

@@

\section{Light Curve Fits}
We fit a two-component model to the light curves. One component models the astrophysical signal (the planet's thermal phase variation and transit), and the other component models the systematic noise introduced by time-dependent changes in instrument performance. For each light curve, we fit the physical and systematic components simultaneously, such that the total observed flux as a function of time is given by $F(t) = F_\mathrm{physical}(t) \times F_\mathrm{sys}(t)$. For the \HST\ data, where we observed two phase curves and two additional eclipses, we constrain the physical parameters to be the same for all visits, but allow some of the systematics parameters to vary (for more details see \S\,\ref{sec:hst_sys}). We fit the WFC3 band-integrated (``white" light curve"), as well as the spectroscopic light curves (FIXME describe).

\subsection{Astrophysical Signal}
We assume the astrophysical signal $F_\mathrm{physical}(t)$ has the following form:
\begin{equation}
	F_\mathrm{physical}(t) = T(t) \times P(t) \times E(t) 
\end{equation}
where $T(t)$ is the transit model, $P(t)$ is the thermal phase variation, $E(t)$ is ellipsoidal variation (change in the apparent radius of the planet with orbital phase due to tidal distortion), and $\alpha(\lambda)$ is the dilution from the companion star (FIXME).

We calculate the transit model with the \texttt{batman} package \citep{kreidberg15a}. The free parameters are the planet radius $r_p$, orbital inclination $i$, the ratio of semi-major axis to stellar radius $a/R_s$, and a linear stellar limb darkening parameter $u$.  We fixed the orbital period to $P = 0.925545613$ day and time of inferior conjunction to $t_0 = 2456836.2964455$, based on estimates from \cite{southworth15}.  We found that the system parameters were poorly constrained for the \HST/WFC3 phase curve (due to incomplete phase coverage) and \Spitzer\ Channel 1 phase curve (due to correlated noise), so for those light curves we fixed the the inclination to $i = 84.54^\circ$ and the semi-major axis to stellar radius $a/R_s  = 2.925$, based on the best fit to the \emph{Spitzer} Channel 2 light curve. (FIXME: looks like we used Southworth?)

@@

@@

@@

@@

>>>>

\author{Tom Louden}
\affiliation{University of Warwick}
\nocollaboration

@@

@@

\section{Light Curve Fits}
We fit a two-component model to the light curves. One component models the astrophysical signal (the planet's thermal phase variation and transit), and the other component models the systematic noise introduced by time-dependent changes in instrument performance. For each light curve, we fit the physical and systematic components simultaneously, such that the total observed flux as a function of time is given by $F(t) = F_\mathrm{physical}(t) \times F_\mathrm{sys}(t)$. For the \HST\ data, where we observed two phase curves and two additional eclipses, we constrain the physical parameters to be the same for all visits, but allow some of the systematics parameters to vary (for more details see \S\,\ref{sec:hst_sys}). We fit the WFC3 band-integrated (``white" light curve"), as well as spectroscopic light curves created from 10 wavelength bins uniformly spaced at $0.05 \mu$m intervals.

\subsection{Astrophysical Signal}
We assume the astrophysical signal $F_\mathrm{physical}(t)$ has the following form:
\begin{equation}
	F_\mathrm{physical}(t) = F_s (1 + \alpha) \times T(t) + F_p(t) 
\end{equation}
where $F_s$ is the stellar flux, $T(t)$ is the transit model (the fraction of the stellar disk that is visible), $\alpha$ is additional fractional flux from the companion star, and $F_p(t)$ is the planet flux. FIXME what is alhpha. The flux from the planet is given by
\begin{equation}
F_p(t) = \pi I(t)[R(t)]^2
\end{equation}
where $I(t)$ is the disk-integrated planet intensity and $R(t)$ is the planet's effective radius (which changes with orbital phase due to tidal distortion).

We calculate the transit model with the \texttt{batman} package \citep{kreidberg15a}. Many of the physical parameters are tightly constrained by \cite{southworth15}, so we fixed the orbital period, time of inferior conjunction, orbital inclination, and ratio of semi-major axis to stellar radius to the previously published values ($P = 0.925545613$ day, $t_0 = 2456836.2964455 \mathrm{BJD_{TDB}}$, $i = 87.3^\circ$, and $a/R_s = 2.999$). As a test, we fit for these parameters with the Spitzer Channel 2 light curve, which has the best phase coverage and least systematic noise of the three data sets. We found that the transit parameters are consistent with the \cite{southworth15} results, so we proceeded with the remainder of the analysis holding those parameters fixed.  The free parameters for the transit model were the transit depth $r_p$ and a linear limb darkening parameter $u$.

@@

\begin{deluxetable}{lllllll}
\tablecolumns{7}
\tablewidth{0pt}:
\tablecaption{Model Comparison \label{table:models}}
\tablehead{
\colhead{Data Set} & \colhead{Model} & \colhead{$T_\mathrm{min}$} & \colhead{$T_\mathrm{max}$} & \colhead{$\chi^2$} & \colhead{$\Delta$ AIC} & \colhead{$\Delta$ BIC}}
\startdata
WFC3 & Sph. Harmonics & 1212 & 3190 & 949.6 & 0.0 & 0.0 \\
\, & Kinematic & 1955 & 3910 & 961.6 & 12.0 & 12.0 \\
\, & Two Temp. & 0 & 2837 & 999.4 & 47.7 & 43.3 \\
Ch 1 & Sph. Harmonics & 1277 & 3442 & 0.9 & 0.0 & 0.0 \\
\, & Kinematic & 1952 & 3672 & 0.9 & 34.3 & 34.3 \\
\, & Two Temp. & 1427 & 3039 & 0.9 & 10.7 & 17.6 \\
Ch 2 & Sph. Harmonics & 930 & 3775 & 1.1 & 0.0 & 3.1 \\
\, & Kinematic & 1719 & 4257 & 1.1 & 14.35 & 17.41 \\
\, & Two Temp. & 1380 & 3305 & 1.1 & 23.9 & 0.0 \\
\enddata
\vspace{-0.8cm}
\tablecomments{comments}
\end{deluxetable}

@@

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/dayside_spectrum.pdf}
\caption{Dayside emission spectrum.}
\label{fig:dayside}
\end{figure}

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{Figures/emission_spectra.pdf}
\caption{Phase-resolved emission spectra.}
\label{fig:spectra}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{Figures/hst_model_comparison.pdf}
\caption{Left: fits to the broadband WFC3 phase curve. Right: best fit temperature maps.}
\label{fig:model_comparison}
\end{figure*}

@@

\section{Comparison of T/P Profiles}
